Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-04-29 markdown/paper.Rmd
Figure out cross referencing of tables

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output:
  pdf_document:
    fig_caption: yes
bibliography: "test.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf"
                     )
library(scales)
library(ggplot2)
library(extrafont)
```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

#Introduction

@@

#Background of Felony Disenfranchisement in the United States

@@

#Academic Literature and Felony Disenfranchisement

@@

#Spatial Effects of Concentrated Policing and Incarceration

@@

##concentrated policing

#Research Design: Spatial Implications of Felony Disenfranchisement in New York City and Miami

##Matching
##Geocoding

#Maps
```{r figs, echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016"}
j <- readRDS("./output/city_map.RDS")
j
```

@@

\newpage
#References

>>>>

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output:
  bookdown::pdf_document2:
    toc: no
bibliography: "citations.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf"
                     )
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(stargazer)
```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

#Introduction {-}

@@

#Background of Felony Disenfranchisement in the United States {-}

@@

#Academic Literature and Felony Disenfranchisement {-}

@@

#Spatial Effects of Concentrated Policing and Incarceration {-}

@@

##concentrated policing {-}

#Research Design: Spatial Implications of Felony Disenfranchisement in New York City and Miami {-}

##Matching {-}
##Geocoding {-}

#Maps {-}
```{r citywide-map, echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016"}
j <- readRDS("./output/city_map.RDS")
j
```

@@

#Match Output {-}

```{r tract-table-chunk, echo = F}
t <- readRDS("./temp/match_table_tract.rds")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:tract-table) Results of Tract-Level Matching", linesep = "") %>% 
  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
j
```

Reg table
```{r tract-reg-chunk, echo = F, results = "asis"}
stargazer(readRDS("./temp/match_reg_tract.rds"),
          header = F,
          type = "latex",
          covariate.labels = c("D(Tract Lost a Voter)", "Constant"),
          dep.var.labels = c("Turnout Rate"),
          title = "(\\#tab:tract-reg) Census Tract Matching Regression",
          table.placement = "H")
```
xxx
```{r block-table-chunk, echo = F}
t <- readRDS("./temp/match_table_block_group.rds")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:blockgroup-table) Results of Block Group-Level Matching", linesep = "") %>% 
  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
j
```

Reg table
```{r block-reg-chunk, echo = F, results = "asis"}
stargazer(readRDS("./temp/match_reg_block_group.rds"),
          header = F,
          type = "latex",
          covariate.labels = c("D(Block Group Lost a Voter)", "Constant"),
          dep.var.labels = c("Turnout Rate"),
          title = "(\\#tab:blockgroup-reg) Census Block Group Matching Regression",
          table.placement = "H")
```
more text

\newpage
#References {-}
